### 2018-11-06 Sections/cryptowars.tex
Statement of controls
minor

\section{Attacks on quantum cryptography}\index{Attacks on quantum cryptography}

@@

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here Eve induces losses in the communications channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it is therefore always possible for lossy channels, and does not introduce any errors.

>>>>

\section{Attacks on quantum cryptography}\index{Attacks on quantum cryptography}\label{sec:attacks_QKD}

@@

A beamsplitting (BS) attack translates the fact that any signal lost over a channel is acquired by Eve. Here Eve induces losses in the communications channel by putting a beamsplitter outside Alice's device, then forwards the remaining photons to Bob. The BS attack does not modify the optical mode that Bob receives: it's therefore always possible for lossy channels, and does not introduce any errors.
